RAS2012: Competition Entry

### 2012-06-12 ras2012-paper/src/main/latex/paper/paper.tex
Make the table smaller.
Updates to the paper.
A better solution.
Newly benchmarked results.
Slowly starting with the paper.

\documentclass[10pt,a4paper,draft]{article}
\usepackage[utf8x]{inputenc}
\usepackage{ucs}
\usepackage[english]{babel}
\usepackage{multirow}
\author{Lukáš Petrovický}
\title{RAS2012: Competition Entry}
\begin{document}

\maketitle
\listoffigures
\listoftables
\tableofcontents

\section{Hello...}

...world!

@@

\input{RDS2.txt-13829.tex}.

>>>>

\documentclass[10pt,a4paper,draft]{article}
\usepackage[utf8x]{inputenc}
\usepackage{ucs}
\usepackage[english]{babel}
\usepackage{multirow}
\usepackage{rotating}
\author{Lukáš Petrovický}
\title{RAS2012: Competition Entry}
\begin{document}

\maketitle

\begin{abstract}
This article describes an entry to the 2012 RAS Problem Solving Competition, concerning dispatching on multi-track territories. The entry is based on the Drools Planner, a Java-based solver. On a reasonably recent computer, the resulting algorithm is able to produce feasible results within a minute and has been fine-tuned to provide best results in under 3 minutes. Source code to the entry is open source and well documented.
\end{abstract}

\section{Introduction}

\section{Describing the solution}

\section{Implementation}

\section{Conclusion}

@@

\section{Resolved systems}

In this section, we show the best solutions reached for each data set. All these were reached within 3 minutes in a single-threaded run, using Intel i7 Q820 processor running Fedora 17 and 1 GB of heap space inside Java 7 runtime environment. The specific solver configurations used to reach these solutions may not have been the same every time.

Please note that via the benchmarking functionality of Drools planner (see above), users may be able to fine-tune the algorithm. This fine-tuning can be focused either on providing better solutions or on faster turnaround times.

\include{RDS1.txt-1582}.

\include{RDS2.txt-8948}.

\include{RDS3.txt-11697}.

\include{TOY.txt-808}.

\section{Visualizations}

\begin{figure}
\centering
\includegraphics[width=150mm,angle=90]{solution.png}
\caption{RAS DATA SET TOY example territory. Undirected graph, arcs have descriptions.}
\end{figure}

\begin{figure}
\includegraphics[width=150mm,angle=90]{B1.png}
\centering
\caption{RAS DATA SET TOY example, route of Train B1. Directed graph where green marks the origin, red the destination and blue is where the train is allowed to wait.}
\end{figure}

In this section, we show examples of visualizations that the solution is capable of providing. These visualizations have been rendered on the fly using the JUNG library\footnote{Java Universal Network/Graph framework, http://jung.sourceforge.net}.
